---
title: "PolymeraseHA_Network"
author: "Sarah Arcos"
date: "2022-11-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(weightedMI)
library(associationsubgraphs)
```

# Calculate the equal-weighted MI for the H3N2 polymerase

## Read in data

```{r}
seq_times <- readRDS("../data/seq_times_091122.rda") %>%
  select(ID = rowname, group = date)
pol <- readMSA("../../H3N2_Processing/polha_aa.fasta")
```

## Calculate MI

 - Uncomment code to actually run
 - **Warning**: for H3N2 pol, takes ~45 min to 1 hour with ncores = 6

```{r}
# polHA_MI <- calculateMI(pol, weighted = TRUE, groups = seq_times,
#                      weights = "equal", ncores = 6)
# 
# saveRDS(polHA_MI, "../data/h3n2polHA_equalMI.rds")
```


## Generate Network Viz

 - Use associationsubgraphs package
 - Set default step to "min_max_rule"
 - Use mi_network_info to get readable index names

```{r}
polHA_MI <- readRDS("../data/h3n2polHA_equalMI.rds")
mi_network_info <- readRDS("../data/mi_network_info.rds")

mi_mean <- mean(polHA_MI$mip)
mi_sd <- sd(polHA_MI$mip)

polHA_MI_z <- polHA_MI %>%
  mutate(z_score = (mip- mi_mean)/mi_sd) %>%
  filter(z_score > 4)

polHA_MI_IDs <- polHA_MI_z %>%
  left_join(mi_network_info, by = c("V1" = "index")) %>%
  left_join(mi_network_info, by = c("V2" = "index")) %>%
  filter(z_score > 4) %>%
  select(a = "id.x", b = "id.y", strength = mip)

visualize_subgraph_structure(
  association_pairs = polHA_MI_IDs,
  node_info = mi_network_info %>% select(-index),
  trim_subgraph_results = FALSE,
  default_step = "min_max_rule"
)

```



## Tally high-scoring MIp among polymerase subunits

 - "High-scoring" means z-score > 4

```{r}
polHA_MI_tallys <- polHA_MI_IDs  %>%
  mutate(grouping = paste(a,b, sep = ", ")) %>%
  mutate(grouping = str_remove_all(grouping, pattern = "_[0-9]*")) %>%
  count(grouping) %>%
  arrange(n) %>% 
  mutate(grouping = factor(grouping, levels = unique(grouping)))

ggplot(polHA_MI_tallys, aes(x = grouping, y = n)) +
  geom_col(alpha = 0.7, fill = "grey") +
  theme_classic() +
  labs(title = "wMI pairs within and between polymerase proteins and HA",
       x = "Group", y = "Count") +
  theme(text = element_text(size = 12),
        legend.position = "none")

# ggsave("../Figures/mipHA_pairs_all.pdf",
#        width = 5, height = 3)

polHA_MI_tallys_summary <- polHA_MI_IDs  %>%
  mutate(group1 = paste(a,b, sep = ", ")) %>%
  mutate(group1 = str_remove_all(group1, pattern = "_[0-9]*")) %>%
  mutate(grouping = case_when(
    group1 %in% c("PB1, HA", "PB2, HA", "PA, HA") ~ "Pol-HA",
    group1 == "HA, HA" ~ "HA-HA",
    TRUE ~ "Pol-Pol"
  )) %>%
  count(grouping) %>%
  arrange(n) %>% 
  mutate(grouping = factor(grouping, levels = unique(grouping)))

ggplot(polHA_MI_tallys_summary, aes(x = grouping, y = n)) +
  geom_col(alpha = 0.7, fill = "grey") +
  theme_classic() +
  labs(title = "wMI pairs within and between polymerase proteins and HA",
       x = "Group", y = "Count") +
  theme(text = element_text(size = 12),
        legend.position = "none")

# ggsave("../Figures/mipHA_pairs_summary.pdf",
#        width = 5, height = 3)
```


